Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-08-20 paper/paper.tex
Incorporate curvilinear effects on g

Long waves induce vertical orbital accelerations, so the short
waves that ride on their surface move in an accelerated reference frame and
experience effective gravitational acceleration that is lower at the crests and
higher in the troughs \cite{longuet1986eulerian,longuet1987propagation}.
A linear wave causes a modulation in gravity acceleration at its surface:

\begin{equation}
\label{eq:gravity_modulation_linear}
\widetilde{g}(\psi) = g + \dfrac{\partial W}{\partial t} = g \left[
  1 - \varepsilon_L e^{\varepsilon_L \cos{\psi}} \left(
    \cos{\psi} - \varepsilon_L \sin^2{\psi}
  \right)
\right]
\end{equation}
The first-order term in $a_L k_L$ is in phase with the long-wave elevation,
so the apparent gravity of the short waves is increased at the long-wave crests
and decreased in the troughs.
The second-order term in $a_L k_L$ is positive-definite and phase-shifted by
$\pi/2$ relative to the crests.
The second-order term thus increases the apparent gravity on the front and rear
faces of the long wave (Fig. \ref{fig:gravity_modulation}).

>>>>

Long waves induce vertical orbital accelerations, so the short
waves that ride on their surface move in an accelerated reference frame and
experience effective gravitational acceleration that is lower at the crests and
higher in the troughs \cite{longuet1986eulerian,longuet1987propagation}.
A long wave modulates gravitational acceleration at its surface:

\begin{equation}
\label{eq:gravity_modulation_general}
\widetilde{g}(\psi)
  = g \cos{\alpha} 
  + \dfrac{\partial W}{\partial t} \cos{\alpha}
  + \frac{\partial U}{\partial t} \sin{\alpha}
\end{equation}
where $\alpha = \arctan{\frac{\partial \eta}{\partial x}}$ is the local slope
of the long-wave surface.
Curvilinear effects on effective gravity can be removed by setting $\alpha = 0$.

For a linear wave, the effective gravity is:

\begin{equation}
\label{eq:gravity_modulation_linear}
\widetilde{g}
  = g 
  \frac{
    1 - \varepsilon_L \cos{\psi} e^{\varepsilon_L \cos{\psi}}
    \left[ 1 + \left(\varepsilon_L \sin{\psi}\right)^2 \right]
  }
  {\sqrt{\left(\varepsilon_L \sin{\psi}\right)^2 + 1}}
\end{equation}

The first-order term in $a_L k_L$ is in phase with the long-wave elevation,
so the apparent gravity of the short waves is increased at the long-wave crests
and decreased in the troughs.
The second-order term in $a_L k_L$ is positive-definite and phase-shifted by
$\pi/2$ relative to the crests.
The second-order term thus increases the apparent gravity on the front and rear
faces of the long wave (Fig. \ref{fig:gravity_modulation}).
